### 2017-08-27 README.Rmd
fix vignette deps

For discrete-valued treatments or exposures:
* The _average treatment effect_ (ATE):
  $$ \Psi_{ATE} = E[E[Y_j \mid A = 1, W_{-j}] - E[Y_j \mid A = 0, W_{-j}]],$$
  where $j$ indexes a target CpG site of interest and $-j$ gives all CpG sites
  in the same neighborhood as the target site except the target site itself
  (i.e., the neighboring sites).

@@

For continous-valued treatments or exposures:
* A _nonparametric variable importance measure_ (NPVI) [@chambaz2012estimation].

>>>>

For discrete-valued treatments or exposures:

* The _average treatment effect_ (ATE):
  $$ \Psi_{ATE} = E[E[Y_j \mid A = 1, W_{-j}] - E[Y_j \mid A = 0, W_{-j}]],$$
  where $j$ indexes a target CpG site of interest and $-j$ gives all CpG sites
  in the same neighborhood as the target site except the target site itself
  (i.e., the neighboring sites).

@@

For continous-valued treatments or exposures:

* A _nonparametric variable importance measure_ (NPVI) [@chambaz2012estimation].
